E Coli Project Paper Incredibly Rough Draft

### 2013-08-31 paper/paper.tex
added stuff to paper Tested everything on node23.

\fixme{our 5 length cells are labeled as 4 cells in the file labels,
  since 4 is the length of the cylinder. In the text I'll refer to the
  5 length cells (file says 4) as 5 length cells.  What huang's paper
  calls 4 length cells will be labeled by our files as 3 length cells,
  but will be refered in our text as 4 length cells}.  We can see a
clear difference in period between the $5\mu$, $4\mu$, and $2\mu$
length cells.  The oscillation periods for our $4\mu$ show excellent
agreement with the simulations of Huang et all
\cite{huang2003dynamic}.  This is to be expected since we begin our
simulations with their reported wild type concentrations of MinD and
MinE proteins. The periods for the different pill lengths are shown in
the table below.  We can see a direct correltation between size and
period, as the proteins must diffuse further in a longer cell before
they accumulate on the opposite wall.
\newline
\newline
Period According to Pill Length
\begin{tabular}{|r|c|c|c|l|}
  \hline
  Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
  \hline
  Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
  \hline
\end{tabular}

@@

\end{figure}
\subsubsection{Randst-96-Star}
The animations seem to relax into a pattern in which the oscillations
go from the smallest corner, out to the other three, and then back to
the smallest corner.  \fixme{There isn't enough data to see properly
  though, need to run for longer.}

\subsubsection{Randst-97-}
The sideways flying saucer pancake shape shows a truly interesting
breakdown of an unstable equilibrium oscillation.  For the first
number of oscillations the maxima trade off right to left, from a high
peak in the leftward compartment to vertically opposed peaks in the
poles of the long axis of the cell.  This is perhaps due to the fact
that the starting density is highly concentrated to the right of a
dividing line that runs parrallel to the right vertical side.  After a
few oscillations the back and forth oscillations tip toward the
vertical direction and the system loses its initial oscillation
pattern.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-600-800-9800-1500}
  \caption{Arrows that connect maxima that are global in space and
    local in time. The arrow heads touch spatial, time maxima and are
    adjecent to the tails of arrows that show the very next spatial,
    time maxima. The protein that is shown is wall attached MinD-ATP.}
  \label{arrow-plot-randst-98-plot}
\end{figure}

The arrow plot shown here is typical of mannik's squished adnormal
shape.  It shows the protein maxima moving through the cell from one
end to the other end, and back again.

>>>>

\fixme{our 5 length cells are labeled as 4 cells in the file labels,
  since 4 is the length of the cylinder. In the text I'll refer to the
  5 length cells (file says 4) as 5 length cells.  What huang's paper
  calls 4 length cells will be labeled by our files as 3 length cells,
  but will be refered in our text as 4 length cells}.  We can see a
clear difference in period between the $5\mu$, $4\mu$, and $2\mu$
length cells.  The oscillation periods for our $4\mu$ show excellent
agreement with the simulations of Huang et all
\cite{huang2003dynamic}.  This is to be expected since we begin our
simulations with their reported wild type concentrations of MinD and
MinE proteins. The periods for the different pill lengths are shown in
the table below.  We can see a direct correltation between size and
period, as the proteins must diffuse further in a longer cell before
they accumulate on the opposite wall.
\newline
\newline
Period According to Pill Length
\begin{tabular}{|r|c|c|c|l|}
  \hline
  Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
  \hline
  Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
  \hline
\end{tabular}
\newline
\newline

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-400-50-0-0-1500}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-200-50-0-0-1500}
  \caption{Average protein density per unit area of wall for the wall
    attached stages of the protein cycle.  Shown in the right, middle,
    and left parts of a 5$\mu m$ by 1$\mu m$ pill shaped cell (above)
    and a 3$\mu m$ by 1$\mu m$ pill shaped cell (below).}
  \label{ave-per-area-plot-pill}
\end{figure}

Figure \ref{ave-per-area-plot-pill} shows the ave protein per unit
area that is wall attached in the middle, right, and left sections of
the pill shaped cell.  This is an important test of the central idea
behind the utility of the Min protein system.  The system is meant to
place Min proteins on the walls in heavier concentrations in the caps
of the cell and lower concentrations in the middle section, so that
the FtZ polymer may build up along the center walls.  We can see from
the plot of the 3$\mu m$ by 1$\mu m$ cell that the MinD proteins reach
concentration peaks in the caps that are roughly three times higher
(for the MinD-ATP proteins) and roughly 1.5 times higher (for the
MinD-MinE-ATP) than peaks in the center.  Integrals of these plotted
values show that the time averaged concentrations are likewise higher
in the caps than in the center.  \fixme{am computing these integrals
  now in ave_plot.py but need to print out into maybe a bar chart}

@@

\end{figure}
\subsubsection{Randst-96-Star}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{total-oscillation-randst-96-plot}
\end{figure}

We haven't simulated long enough yet, so no real pattern has shown
itself.  There's certainly oscillations, and it's almost as if there's
competing modes - top to bottom, left to right, corner to corner, etc.
Interesting.

\fixme{maybe?}The animations seem to relax into a pattern in which the oscillations
go from the smallest corner, out to the other three, and then back to
the smallest corner?  \fixme{There isn't enough data to see properly
  though, need to run for longer.}

\subsubsection{Randst-97-}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the sideways flying saucer
    pancake cell shape.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{total-oscillation-randst-97-plot}
\end{figure}

The sideways flying saucer pancake shape shows a truly interesting
breakdown of an unstable equilibrium oscillation.  For the first
number of oscillations the maxima trade off right to left, from a high
peak in the leftward compartment to vertically opposed peaks in the
poles of the long axis of the cell.  This is perhaps due to the fact
that the starting density is highly concentrated to the right of a
dividing line that runs parrallel to the right vertical side.  After a
few oscillations the back and forth oscillations tip toward the
vertical direction and the system loses its initial oscillation
pattern.  The total MinD animation shows that it falls quickly instead into a
back and forth pattern between the two opposing endcaps, skipping
right over the middle indentation.  The oscillation at this point is
reminiscent of the pills shape oscillation, showing the robust nature
of the back and forth pattern.

Figure \ref{total-oscillation-randst-97-plot} shows between the top
right and top left sections a pattern very close to the pattern seen
in the pill shaped oscillations, with sharp spikes in wall attached
MinD-ATP followed by lesser spikes in wall attached MinD-MinE-ATP,
follwed by the other end showing a similar behavoir pi radius later.
It is interesting to observe the middle section and the middle
leftward indentation as well.  It can be seen that the MinD-ATP shows
moderate spikes in between the spikes on the top and the bottom,
showing that the proteins are traveling through this section, but
interestingly the left middle indentation shows this spike
consistently later than the right middle section. As the protein
travels back and forth through the cell, there is a certain amount of
lag in the middle indentation.  The system gets caught there for a
little bit before moving on.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-600-800-9800-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-D_ND-randst-25-600-800-9800-1500}
  \caption{(above) Arrows that connect maxima that are global in space
    and local in time. The arrow heads touch spatial, time maxima and
    are adjecent to the tails of arrows that show the very next
    spatial, time maxima. (below) An time averaged plot of the same
    proteins in the same cells shape.  The protein that is shown is
    wall attached MinD-ATP.}
  \label{arrow-plot-randst-98-plot}
\end{figure}

The arrow plot shown here is typical of mannik's squished adnormal
shape.  It shows the protein maxima moving through the cell from one
end to the other end, and back again.  The effect of this movement can
be seen in the time averaged plot directly below the arrow plot.  The
proteins spend a majority of time at the very ends of the cell.
